\begin{center} \bf \sffamily \LARGE Prisoner's dilemma with stochastic payoffs\\[-1cm] \end{center}

### 2023-02-23 paper/main.tex
removes main from root

So far we have explored the difference between the expected payoffs and the last
round payoffs. In order to explore further the effect of limited memory we allow
individuals to remember more. More precisely, up to two interactions and up to
the last two rounds. In total we present results for three more updating
payoffs. These are the payoffs when individuals consider the last two rounds
with another member of the population, the last round with two members of the
population, and the last two rounds with two members of the population. Similar
to the last round payoff, we use simulations and record which strategies the
players adopt over time based
% (Appendix~\ref{appendix:further_simulation_results}) and we compare the evolving
% cooperation rates to those of the expected payoffs
% (Figure~\ref{fig:cooperation_rates_two_by_two_part_two}).

\begin{figure}[!htbp]
  \centering
  \includegraphics[width=\textwidth]{static/more_memory_summary_results.pdf}
  \caption{{\bf Average cooperation rates for different updating payoffs.} (From
  right to left) updating Payoffs based  on perfect memory, limited memory,
  the last round payoff of two interactions,
  the last two rounds payoff of one interaction and 
  the last two round payoffs of two interactions.({\bf High Benefit})
  ({\bf Low Benefit}) We vary the selection strength $\beta$. In all
  cases, stochastic payoff evaluation tends to reduce the evolving cooperation
  rates. Unless explicitly varied, the parameters of the simulation are
  $N\!=\!100$, $b\!=\!3$, $c\!=\!1$, $\beta\!=\!1$, $\delta\!=\!0.99$.
  Simulations are run for $T\!=\!5\times 10^7$ time steps for each parameter
  combination.}\label{fig:cooperation_rate_updating_payoffs}
\end{figure}

>>>>

So far we have explored the difference between the expected payoffs and the last
round payoffs. To explore further the effect of limited memory we consider three
more cases. These are the cases where the updating payoffs depend on  the last
round with two members of the population, the last two rounds with another
member of the population, and the last two rounds with two members of the
population. Similar to the last round payoff. The details of each approach can
be found in the Supplementary Information. We use numerical simulation of the
pairwise process for the various schemes. The results for low and high benefit
are shown in Figure~\ref{fig:cooperation_rate_all_updating_payoffs}.

\begin{figure}[!htbp]
  \centering
  \includegraphics[width=\textwidth]{static/more_memory_summary_results.pdf}
  \caption{{\bf Average cooperation rates for different updating payoffs.}
  From left to right, we present result on the following updating payoffs cases;
  (1) the expected payoffs (perfect memory), (2) the last round payoff from one
  interaction (limited memory), (3) the last round payoff from two interactions,
  (4) the last two rounds payoffs from one interaction, (5) the last two rounds
  payoffs from two interactions. The details of each case are given in the
  Supplementary Information. Cases 3 and 4 have similar results. In that the
  evolved generosity is the same. For cases 2 - 5 the cost benefit ratio
  has an effect compared to the limited memory case. The cooperation rate
  increases, and as we allow for more information the closer we move to the
  perfect memory. Unless explicitly varied, the parameters of the simulation are
  $N\!=\!100$, $b\!=\!3$, $c\!=\!1$, $\beta\!=\!1$, $\delta\!=\!0.99$.
  Simulations are run for $T\!=\!5\times 10^7$ time steps for each parameter
  combination.}\label{fig:cooperation_rate_all_updating_payoffs}
\end{figure}
